Appendix of Bauer et al. (2023) Dike experiment

### 2023-02-21 manuscript_appendix.Rmd
Update manuscript_appendix.Rmd

## Appendix A1 {.unnumbered}

Three dry years (2018--2020) and three minor floods (2018, 2019, 2021) occurred during the study period. Annual temperature, precipitation and discharge of River Danube near the study sites (2017--2021), based on weather station Metten [mean, 1981--2010; ID, 3271; WGS84, lat/lon, 48.85476, 12.918911; @cdc2022prec, @cdc2022temp] and stream gauge Pfelling [ID, 10078000; WGS84, lat/lon, 48.87975, 12.74716; @lfu2021discharge]. HQ2 = Highest discharge with a probability of occurrence every second year. HSW = Highest water level for shipping.

@@

## Appendix A2 {.unnumbered}

Describe what it is and where it can be found <!--# Is it cited in teh text? Write more and explain location -->

## Appendix A3 {.unnumbered}

@@

>>>>

# Appendix A1

Three dry years (2018--2020) and three minor floods (2018, 2019, 2021) occurred during the study period. Annual temperature, precipitation and discharge of River Danube near the study sites (2017--2021), based on weather station Metten [mean, 1981--2010; ID, 3271; WGS84, lat/lon, 48.85476, 12.918911) @cdc2022temp, @cdc2022prec] <!--# Check brackets -->and stream gauge Pfelling [ID: 10078000, WGS84, lat/lon, 48.87975, 12.74716, @lfu2021discharge]. HQ2 = Highest discharge with a probability of occurrence every second year. HSW = Highest water level for shipping.

@@

# Appendix A2

All sown seed mixtures can be found on GitHub in the folder \`outputs/tables/table_a2_seed_mixtures.csv\`. There it is indicated which species are combined and the ratio in the specific seed mixture.

# Appendix A3

@@

# Appendix A4

All species which occurred 2018--2021 and the amount of plots in which they appeared (maximum 1152 = 4 years times 288 experimental plots). In total, 274 different species were found. The shades of grey indicate the amount of established plots.

```{r tab.id = "specieslist", tab.cap = ""}
read_csv(
  here("outputs", "tables", "table_a4_specieslist.csv"),
  col_names = TRUE,
  na = c("na", "NA"),
  col_types = cols(.default = "?", name = "f")
  ) %>%
  mutate(name = str_replace_all(name, "_", " ")) %>%
  rename(Name = name, "Presence [# plots]" = sum) %>%
  flextable() %>%
  align(part = "all", align = "center", j = -1) %>%
  bold(part = "header") %>%
  style(j = 1, pr_t = fp_text_default(italic = TRUE)) %>%
  bg(j = 2, bg = scales::col_numeric(palette = c("white", "grey60"), domain = c(0, 931))) %>%
  autofit()
```
